Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
wordsmithing in 5

Finally, we can define our core properties. They can be found in \cref{tab:props},
arranged to show their commonalities and distinctions. Each definition gives a criterion
quantified over states \(s\) that immediately follow call steps.
If an execution can reach a state \(s'\) such that \(s' \stepstounder{\overline{\psi}} s\)
where \(\mathbf{call} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then \(s\) is the target
of a call.
%Likewise, if \(\mathbf{tailcall} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then
%\(s\) is the target of a tailcall.
As a shorthand, we write that each property is defined
by a criterion that must hold ``for all call targets \(s\).'' In the case of \(\wbcf\),
we also need to know about the callee, so we refer to the ``call step \(s \stepstounder{} s'\).

\paragraph*{\(\wbcf\)}
Given a call step \((\mach,(V,\sigma)) \stepstounder{} (\mach',(V',\sigma'))\),
we define the predicate \(\ret\) to hold on states \(\mach''\)
whose stack pointer matches that of \(\mach\)
and whose program counter is at the next instruction. We enjoy \(\wbcf\) if
\(\ret\) holds on return from \(\mach'\).

\paragraph*{\(\clri\)}
When our call target is \((\mach,(V,\sigma))\), we define the predicate \(\intProp\) to hold
on states \(\mach'\) if any elements that are both sealed in \(V\) and in the difference
set between \(\mach\) and \(\mach'\) are irrelevant. We enjoy \(\clri\) if \(\intProp\)
holds on return from \(\mach\).

\paragraph*{\(\clrc\)}
When our call target \((\mach,(V,\sigma))\), we begin by taking an arbitrary \(\nach\)
that is a \(\components\)-variant of \(\mach\), where \(\components\) is the set of sealed elements
in \(V\). We require that two clauses hold. On line a, the behavior of a trace from
\((\mach,(V,\sigma))\) up to its return must match that of \((\nach,(V,\sigma))\).
On line b, we define a relation \(\confProp\) that relates states \(\mach'\) and \(\nach'\)
if their corrupted set (relative to \(\mach\) and \(\nach\)) is irrelevant, and require
that it hold on the returns from \((\mach,(V,\sigma))\) and \((\nach,(V,\sigma))\).
We enjoy \(\clrc\) if both clauses hold.

\paragraph*{\(\clec\)}
We consider the callee's private behavior to be any changes that it makes to the state
outside of legitimate channels---elements marked \(\object\) or \(\public\). The remainder
should be kept secret, which is to say, irrelevant. Similar to \(\clri\), given a call target
\((\mach,(V,\sigma))\), we define a predicate \(\cconfProp\) to hold
on states \(\mach'\) if the difference set between \(\mach\) and \(\mach'\), that is
not \(\object\) or \(\public\), is irrelevant. If \(\cconfProp\) holds on return,
we enjoy \(\clec\).

\paragraph*{\(\clei\)}
Callee integrity means that the caller does not influence it outside of legitimate
channels. The caller's influence can be seen internally, or in corrupted data on return,
just like the caller's secrets would under \(\clrc\). So, for a call target
\((\mach,(V,\sigma))\), we take an arbitrary \(\nach\) that is a \(\components\)-variant
of \(\mach\), where \(\components\) is the set all elements that are not \(\object\)
or \(\public\). The remainder of the property is identical to \(\clrc\).

@@

The system we model in \cref{sec:example,sec:formal} is very simple, but our properties
are designed to make it easy to add features. To support argument passing on the stack,
we just new parameters to the existing security-relevant operations, and refine how they
update the security context. The remainder of the properties do not change at all.
To add tail-calls, we add and define a new operation, and since it is a kind of call,
we add it to the definition of call targets again.
The rules for the expanded machine are given in \cref{fig:advops}; the
rules in \cref{fig:basicops} can be recaptured by instantiating
\(\mathbf{call}\) with \(\overline{sa}\) as the empty set, and \(\mathbf{alloc}\)
with flag \(\mathbf{f}\).

>>>>

\subsection{Properties}

Finally, the core property definitions are given in \cref{tab:props},
arranged to show their commonalities and distinctions. Each definition gives a criterion
quantified over states \(s\) that immediately follow call steps.
If an execution includes a transition \(s' \stepstounder{\overline{\psi}} s\)
where \(\mathbf{call} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then \(s\) is the target
of a call.
%Likewise, if \(\mathbf{tailcall} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then
%\(s\) is the target of a tailcall.
As a shorthand, we write that each property is defined
by a criterion that must hold ``for all call targets \(s\),'' or, in the case of \(\wbcf\),
``for all call steps \(s \stepstounder{} s'\).''

\paragraph*{1.~\(\wbcf\)}
Given a call step \((\mach,(V,\sigma)) \stepstounder{} (\mach',(V',\sigma'))\),
we define the predicate \(\ret\) to hold on states \(\mach''\)
whose stack pointer matches that of \(\mach\)
and whose program counter is at the next instruction. A system enjoys \(\wbcf\) if,
for every call transition, \(\ret\) holds just after the callee returns (i.e.,
the call stack shrinks).

\paragraph*{2.~\(\clri\)}
When the call target is \((\mach,(V,\sigma))\), we define the predicate \(\intProp\) to hold
on states \(\mach'\) if any elements that are both sealed in \(V\) and in the difference
set between \(\mach\) and \(\mach'\) are irrelevant. A system enjoys \(\clri\) if, for every
call, \(\intProp\) holds just after the corresponding return.

\paragraph*{3.~\(\clrc\)}
When the call target is \((\mach,(V,\sigma))\), we begin by taking an arbitrary \(\nach\)
that is a \(\components\)-variant of \(\mach\), where \(\components\) is the set of sealed elements
in \(V\). We require that two clauses hold. On line 3a, the behavior of a trace from
\((\mach,(V,\sigma))\) up to its return must match that of \((\nach,(V,\sigma))\).
On line 3b, we define a relation \(\confProp\) that relates states \(\mach'\) and \(\nach'\)
if their corrupted set (relative to \(\mach\) and \(\nach\)) is irrelevant, and require
that it hold just after the returns from the callees that start at \((\mach,(V,\sigma))\) and \((\nach,(V,\sigma))\).
A system enjoys \(\clrc\) if both clauses hold for every call.

\paragraph*{4.~\(\clec\)}
We consider the callee's private behavior to be any changes that it makes to the state
outside of legitimate channels---elements marked \(\object\) or \(\public\). The remainder
should be kept secret, which is to say, irrelevant to future execution. Similar to \(\clri\), given a call target
\((\mach,(V,\sigma))\), we define a predicate \(\cconfProp\) to hold
on states \(\mach'\) if the difference set between \(\mach\) and \(\mach'\), excluding 
\(\object\) or \(\public\) locations, is irrelevant.
A system enjoys \(\clec\) if, for every call, \(\cconfProp\) holds just after the corresponding return.

\paragraph*{5.~\(\clei\)}
Callee integrity means that the caller does not influence it outside of legitimate
channels. The caller's influence can be seen internally, or in corrupted data on return,
just like the caller's secrets would be under \(\clrc\). So, for a call target
\((\mach,(V,\sigma))\), we take an arbitrary \(\nach\) that is a \(\components\)-variant
of \(\mach\), where \(\components\) is the set all elements that are not \(\object\)
or \(\public\). The remainder of the property is identical to \(\clrc\).

@@

The system we model in \cref{sec:example,sec:formal} is very simple, but our properties
are designed to make it easy to add features. To support argument passing on the stack,
we just new parameters to the existing security-relevant operations, and refine how they
update the security context. The remainder of the properties do not change at all.
To add tail-calls, we add and define a new operation, and since it is a kind of call,
we add it to the definition of call targets.
The rules for the expanded machine are given in \cref{fig:advops}; the
rules in \cref{fig:basicops} can be recaptured by instantiating
\(\mathbf{call}\) with \(\overline{sa}\) as the empty set, and \(\mathbf{alloc}\)
with flag \(\mathbf{f}\).
